showData 4

### 2016-11-07 CreateData/showData4.Rmd
find 18000 deaths

---
title: "showData 4"
author: "Göran Broström"
date: "September 22, 2016"
output: pdf_document
fontsize: 11pt
---

@@

```{r frominddata}
load("data/inddata.rda")
load("data/sex.rda")
indx <- match(inddata$LINNEID, sex$LINNEID)
inddata$KON <- sex$KON[indx]
per <- inddata[!is.na(inddata$KON) & (inddata$FODELSEAR < 1975), ]
per$birthdate <- per$FODELSEAR + 0.125  +  (per$FODELSEKVARTAL - 1) / 4
```

@@

```{r styronper}
load("data/socstyr.rda")
indx <- match(per$LINNEID, socstyr$LINNEID)
per$DODSDAT <- socstyr$DODSDAT[indx]
fixd <- !is.na(per$DODSDAT) & (per$DODSDAT < 1960010)
per$DODSDAT[fixd] <- per$DODSDAT[fixd] * 100 + 15
per$deathdate <- as.numeric(skum::tillTid(per$DODSDAT))
per$dodsKOMMUN <- socstyr$KOMMUN[indx]
per$dodsALDER <- socstyr$ALDER[indx]
per$ULORSAK <- socstyr$ULORSAK[indx]
```

@@

```{r fob60}
load("data/fob.rda")
fob60 <- fob[fob$AR == 1960 & 
                 fob$KOMMUN %in% ourkom &
                 fob$LINNEID %in% per$LINNEID, ]
```

@@

@@

```{r mat90}
library(eha)
indx <- match(fob90$LINNEID, per$LINNEID)
fob90$birthdate <- per$birthdate[indx]
lim <- as.numeric(toTime("1960-11-01"))
fob90 <- fob90[fob90$birthdate < lim, ]
indx <- match(fob90$LINNEID, per$LINNEID) # NOTE: Necessary!
fob90$enter <- lim + 20 - fob90$birthdate
##fob90$enter <- as.numeric(toTime("1985-11-01")) - fob85$birthdate
dd <- per$deathdate[indx]
fob90$event <- !(is.na(dd)) & (dd <= lim + 20)
##fob90$event <- !(is.na(dd)) & (dd < 1987) 
fob90$exit <- fob90$enter + 10  ## Not any longer: 1 year and 2 months.
fob90$exit[fob90$event] <- dd[fob90$event] - fob90$birthdate[fob90$event]
fob90 <- fob90[fob90$exit > fob90$enter, ] # Shouldn't be necessary!
head(fob90)
##cat("lim = ", lim, "\n")
```

@@

```{r lisadat}
load("data/lisa.rda")
lisa <- lisa[lisa$KOMMUN %in% ourkom, ]
indx <- match(lisa$LINNEID, per$LINNEID)
lisa$birthdate <- per$birthdate[indx]
```

>>>>

---
title: "showData 4"
author: "Göran Broström"
date: "November 5, 2016"
output: pdf_document
fontsize: 11pt
---

@@

```{r frominddata}
load("~/Forskning/Data/inddata.rda")
load("~/Forskning/Data/sex.rda")
indx <- match(inddata$LINNEID, sex$LINNEID)
inddata$KON <- sex$KON[indx]
per <- inddata[!is.na(inddata$KON) & (inddata$FODELSEAR < 1975), ]
per$birthdate <- per$FODELSEAR + 0.125  +  (per$FODELSEKVARTAL - 1) / 4
```

@@

```{r styronper}
load("~/Forskning/Data/socstyr.rda")
indx <- match(per$LINNEID, socstyr$LINNEID)
per$DODSDAT <- socstyr$DODSDAT[indx]
fixd <- !is.na(per$DODSDAT) & (per$DODSDAT < 1960010)
per$DODSDAT[fixd] <- per$DODSDAT[fixd] * 100 + 15
per$deathdate <- as.numeric(skum::tillTid(per$DODSDAT))
per$dodsKOMMUN <- socstyr$KOMMUN[indx]
per$dodsALDER <- socstyr$ALDER[indx]
per$ULORSAK <- socstyr$ULORSAK[indx]
save(per, file = "data4/per.rda")
```

@@

```{r fob60}
load("~/Forskning/Data/fob.rda")
fob60 <- fob[fob$AR == 1960 & 
                 fob$KOMMUN %in% ourkom &
                 fob$LINNEID %in% per$LINNEID, ]
```

@@

**Update 2016-11-05:** Draw it to December 31, 2001, i.e. add 14 months! Reason: 
No hisclass in LISA before 1 Jan 2002!

@@

```{r mat90}
library(eha)
indx <- match(fob90$LINNEID, per$LINNEID)
fob90$birthdate <- per$birthdate[indx]
lim <- as.numeric(toTime("1970-11-01"))
fob90 <- fob90[fob90$birthdate < lim, ]
indx <- match(fob90$LINNEID, per$LINNEID) # NOTE: Necessary!
fob90$enter <- lim + 20 - fob90$birthdate
##fob90$enter <- as.numeric(toTime("1985-11-01")) - fob85$birthdate
dd <- per$deathdate[indx]
fob90$event <- !(is.na(dd)) & (dd <= lim + 31 + 61 / 365)
##fob90$event <- !(is.na(dd)) & (dd < 1987) 
fob90$exit <- fob90$enter + 10 + 1 + 61 / 365 ## 10 + 1 + nov, dec: 1 year and 2 months.
fob90$exit[fob90$event] <- dd[fob90$event] - fob90$birthdate[fob90$event]
fob90 <- fob90[fob90$exit > fob90$enter, ] # Shouldn't be necessary!
head(fob90)
##cat("lim = ", lim, "\n")
```

@@

```{r lisadat}
load("~/Forskning/Data/lisa.rda")
lisa <- lisa[lisa$KOMMUN %in% ourkom, ]
indx <- match(lisa$LINNEID, per$LINNEID)
lisa$birthdate <- per$birthdate[indx]
```
